\documentclass{../signatures}
\labacronym{RUT}
\labtitle{Rutherford Scattering}

\begin{document}

\maketitle

\names

\textbf{Before the Lab}

You must watch the Radiation Safety video, and get a Radiation Ring before you use the apparatus in this experiment. View the Rutherford video about this experiment online.
\\[24pt]

Ring \# $\rule{1cm}{0.15mm}$  Issued (Date and Signed) $\rule{3cm}{0.15mm}$  Returned (Date and Signed) $\rule{3cm}{0.15mm}$
\\[12pt]

\prelab

\begin{enumerate}

    \item Describe Rutherford scattering. Read the following: Book by A. C. Melissinos, "Experiments in Modern Physics", Academic Press, New York, 2003, the section on Rutherford Scattering.
    
    \item What is the Rutherford scattering formula? Define or explain each of the terms in the formula. What is a scattering cross section? How is the cross section related to what you actually measure in the experiment?

    \item Why is it difficult to obtain data at large scattering angles?
       \\[36pt]
\end{enumerate}

\prelabsignatures

\midlab

\begin{enumerate}

    \item By day 4 you should have enough data to demonstrate the angular dependence of Rutherford scattering. Show it to an instructor and ask for a signature.
\\[36pt]
\end{enumerate}

\midlabsignatures{4}

\checkpointsection 

\begin{enumerate}

\item \checkp{Preparation}

\item \checkp{Peak Finding}

\item \checkp{Additional Questions}

\item \checkp{Zeeman Picture}

\item \checkp{Zeeman Splitting}

\end{enumerate}

\end{document}